Title---**Data Science Capstone project**
Date----11/26/2021
Author---Shivangi Mehta.

##Load all the packages.

```{r,warning=FALSE,error=TRUE}
library(quanteda)
require(readtext)
library(sqldf)
install.packages("stringi")
library(stringi)
library(ggplot2)
```

##Introduction.

The goal of the project is to build a predictive model for suggesting next word given a text input.In this report we will summarise data exploration for next word prediction model. Dataset consists of corpus in English, German and finnish.We will focus on english text for this project.We will use data from https://d396qusza40orc.cloudfront.net/dsscapstone/dataset/Coursera-SwiftKey.zip.
Data consists of three corpora from blogs, new and twitter sites. 
Lets load and explore the data.

```{r,warning=FALSE,error=TRUE}
conn <- file("./data/final/en_US/en_US.twitter.txt", "r")
twitterText <- readLines(conn, encoding = "UTF-8", skipNul = TRUE)
close(conn) 
conn <- file("./data/final/en_US/en_US.news.txt", "r")
newsText <- readLines(conn, encoding = "UTF-8", skipNul = TRUE)
close(conn)
conn <- file("./data/final/en_US/en_US.blogs.txt", "r")
blogsText <- readLines(conn, encoding = "UTF-8", skipNul = TRUE)
close(conn) 

```

###Lets check the no of lines, words and size of all three texts: 

```{r,warning=FALSE,error=TRUE}
sizeTwitter <- file.info("./data/final/en_US/en_US.twitter.txt")$size / 1024
sizeNews <- file.info("./data/final/en_US/en_US.news.txt")$size / 1024
sizeblogs <- file.info("./data/final/en_US/en_US.blogs.txt")$size / 1024
wordsTwitter <- stri_count_words(twitterText)
wordsNews <- stri_count_words(newsText)
wordsbolg <- stri_count_words(blogsText)
data.frame(Source = c("Twitter", "News", "Blogs"),
           SizeMB = c(sizeTwitter, sizeNews, sizeblogs),
           NoofLines = c(length(twitterText),length(newsText), length(blogsText)),
           NoOfWords = c(sum(wordsTwitter),sum(wordsNews),sum(wordsbolg)))
```

#### Data sampling.

Due to memory limitation we will use a sample of the data for our modelling. 
I have merged data from all three files into a consolidated file and we will sample 15% lines from this file.
We will put the result in another file and load it into a corpus object.

```{r,warning=FALSE,error=TRUE}
set.seed(1288)
twitter_sample <- sample(twittertxt, length(twittertxt)*0.01, replace = FALSE)
blogs_sample <- sample(blogstxt, length(blogstxt)*0.01, replace = FALSE)
news_sample <- sample(newstxt, length(newstxt)*0.01, replace = FALSE)
Sample_data <- c(twitter_sample, blogs_sample, news_sample)

```

##Helpher Method.

```{r,warning=FALSE,error=TRUE}
getProfanities <- function() {
  profanityFile <- "profanities.txt"
  if (!file.exists(profanityFile)) {
    download.file('http://www.cs.cmu.edu/~biglou/resources/bad-words.txt',
                  profanityFile)
  }
  profanities <-
    read.csv("profanities.txt",
             header = FALSE,
             stringsAsFactors = FALSE)
  profanities$V1
}

makeNgrams <- function(sentences, n = 1L) {
  words <-
    tokens(
      sentences,
      ngrams = n,
      remove_url = TRUE,
      remove_separators = TRUE,
      remove_punct = TRUE,
      remove_twitter = TRUE,
      what = "word",
      remove_hyphens = TRUE,
      remove_numbers = TRUE
    )
  words <-  tokens_remove(words, getProfanities())
}
plotMostFrequentwords <- function(nGrams, title){
  nGramList <-  unlist(nGrams, recursive = FALSE, use.names = FALSE)
   wordFreq <- table(nGramList)
   mostfreqTwoGrams <- as.data.frame(sort(wordFreq,decreasing=TRUE)[1:10])
   ggplot(mostfreqTwoGrams, aes(x= nGramList,y = Freq)) +geom_bar(stat = "identity") +
     theme(axis.text.x = element_text(angle = 90, hjust = 0))  + ggtitle(title)
}
```

####Data cleanup.

Any text prediction algorithm has to deal with offensive words.
Then we will create n-grams and remove the profanities using tokens_remove feature of quanteda.
We will use the list of bad words available at http://www.cs.cmu.edu/~biglou/resources/bad-words.txt.

```{r,results='hide'}
sentences <-
    quanteda::tokens(
      Sample_data,
      what = "sentence",
      remove_punct = TRUE,
      remove_twitter = TRUE
    )
sentences <-tokens_remove(sentences, getProfanities())
sentences <- unlist(lapply(sentences, function(a)
     char_tolower(a)))
corp <- corpus(c(
  d1 = "Line 1.\nLine 2.\nLine Three.\n",
  d2 = "Sentence One.\nSentence Two.\n\nLast sentence."
))
cs1 <- corpus_segment(corp, ".", pattern_position = "before")
cs1
  twoGrams <- makeNgrams(cs1, 2)
  threeGrams <- makeNgrams(cs1, 3)
   FourGrams <- makeNgrams(cs1, 4)
```

##### Exploratory analysis 

```{r}
plotMostFrequentwords(twoGrams, "Top 10 bigrams")
plotMostFrequentwords(threeGrams, "Top 10 trigrams")
plotMostFrequentwords(FourGrams, "Top 10 quadGrams")
```

## Next steps

Now we will create nGram model for predicting next words and deploy it in a shiny app.
  